### 2020-02-17 ordinal/ordinal.Rmd
ordinal html

```{r echo=T,results="show"}
delta2 = as.data.frame(t(apply(exp(s2[['delta_fixed[1,1]']] +
                                   s2[, grep('delta_random_1', names(s2))]), 2, sumfun)))
ggplot(data.frame(delta = delta2), aes(sample = delta)) +
    stat_qq() +
    ylab('Sample quantile of log(d\') = delta random effects') +
    xlab('Theoretical normal quantile') +
    labs(title = 'SDT model')
```

>>>>

```{r echo=T,results="show"}
delta2 = apply(s2[['delta_fixed[1,1]']] + s2[, grep('delta_random_1', names(s2))], 2, mean)
ggplot(data.frame(delta = delta2), aes(sample = delta)) +
    stat_qq() +
    ylab('Sample quantile of log(d\') = delta random effects') +
    xlab('Theoretical normal quantile') +
    labs(title = 'SDT model')
```
